\bibitem{reg401} https://www.ibm.com/topics/mobile-application-development

\bibitem{reg402} Platzhalter

\bibitem{reg403} Pieter Kubben, Michel Dumontier, Andre Dekker. Fundamentals of Clinical Data Science. Springer Nature Switzerland AG, 2019. [Online]. Available: \url{https://library.oapen.org/bitstream/handle/20.500.12657/22918/1007243.pdf?sequence=1}

\bibitem{reg404} Mohit Singh, Shobha G. Comparative Analysis of Hybrid Mobile App Development Frameworks. International Journal of Soft Computing and Engineering (IJSCE). Volume-10 Issue-6, July 2021 [Online]. Available: \url{https://www.researchgate.net/profile/Mohit-Singh-23/publication/353522485_Comparative_Analysis_of_Hybrid_Mobile_App_Development_Frameworks/links/61603f66ae47db4e57a86fbf/Comparative-Analysis-of-Hybrid-Mobile-App-Development-Frameworks.pdf}

\bibitem{reg405} Cross-platform mobile frameworks used by software developers worldwide from 2019 to 2021 [Graph], JetBrains, July 16, 2021. [Online]. Available: \url{https://www.statista.com/statistics/869224/worldwide-software-developer-working-hours/}

\bibitem{reg406} Lukas Dagne. Flutter for cross-platform App and SDK development. Metropolia University of Applied Sciences, 2019. [Online]. Available: \url{https://www.theseus.fi/bitstream/handle/10024/172866/Lukas Dagne Thesis.pdf}

\bibitem{reg407} \url{https://docs.flutter.dev/development/ui/interactive}

\bibitem{reg408} \url{https://api.flutter.dev/flutter/widgets/State-class.html}

\bibitem{reg409} \url{https://api.flutter.dev/flutter/widgets/InheritedWidget-class.html}

\bibitem{reg410} \url{https://docs.flutter.dev/development/data-and-backend/state-mgmt/simple}

\bibitem{reg412} \url{https://dart.dev/codelabs/async-await}

\bibitem{reg413} \url {https://www.ibm.com/docs/en/cics-ts/5.3?topic=protocol-http-requests}

\bibitem{reg414} \url {https://support.microsoft.com/en-us/topic/maximum-url-length-is-2-083-characters-in-internet-explorer-174e7c8a-6666-f4e0-6fd6-908b53c12246#:~:text=If}

\bibitem{reg415} \url {https://www.sqlite.org/about.html}

\bibitem{reg416} \url {https://pub.dev/packages/get_storage}

\bibitem{reg417} Wenhao Wu. React Native vs Flutter, cross-platform mobile application frameworks. Metropolia University of Applied Sciences, 2018. [Online]. Available: \url{https://www.theseus.fi/bitstream/handle/10024/146232/thesis.pdf}

\bibitem{reg418} \url{https://dart.dev/overview}

\bibitem{reg419} \url{https://www.oracle.com/webfolder/technetwork/tutorials/obe/java/gc01/index.html}

\bibitem{reg421} \url{https://medium.com/flutter/flutter-dont-fear-the-garbage-collector-d69b3ff1ca30}

\bibitem{reg422} \url{https://dart.dev/guides/language/type-system}

\bibitem{reg423} \url{https://docs.flutter.dev/resources/architectural-overview}

\bibitem{reg424}
\bibitem{reg425}
\bibitem{reg426}
\bibitem{reg427}
\bibitem{reg428}
\bibitem{reg429}
\bibitem{reg430}